\documentclass[10pt]{amsart}
\usepackage[margin=1.4in]{geometry}
\usepackage[usenames,dvipsnames,cmyk]{xcolor} %load first
\usepackage{cancel}
\usepackage{graphicx,subfig}
\graphicspath{ {./images/} }

\usepackage{amssymb,amsmath,enumitem,url}

\newcommand{\D}{\mathrm{d}}
\newcommand{\I}{\mathrm{i}}
\DeclareMathOperator{\E}{e}
\DeclareMathOperator{\OO}{O}
\DeclareMathOperator{\oo}{o}
\DeclareMathOperator{\erfc}{erfc}
\DeclareMathOperator{\real}{Re}
\DeclareMathOperator{\imag}{Im}
\usepackage{tikz}
\usepackage[framemethod=tikz]{mdframed}
\theoremstyle{nonumberplain}

\mdtheorem[innertopmargin=-5pt]{sol}{Solution}
%\newmdtheoremenv[innertopmargin=-5pt]{sol}{Solution}
\definecolor{MichiganBlue}{HTML}{00274C}
\definecolor{MichiganYellow}{HTML}{FFCB05}  
\definecolor{NicePurple}{RGB}{75,56,76} %PrincePurple
\definecolor{NiceRed}{RGB}{230,37,52}
\definecolor{MidnightBlue}{rgb}{0.1, 0.1, 0.44}
\usepackage[colorlinks=true, linkcolor=MidnightBlue, citecolor=MidnightBlue, urlcolor=MidnightBlue]{hyperref}

\begin{document}
\pagestyle{empty}

\newcommand{\mline}{\vspace{.2in}\hrule\vspace{.2in}}

\noindent
\text{Hunter Lybbert} \\
\text{Student ID: 2426454} \\
\text{10-21-24} \\
\text{AMATH 567} \\

\title{\bf { Homework 4} }


\maketitle
\noindent
Collaborators*: TODO \\
\\
\tiny
\text{*Listed in no particular order. And anyone I discussed at least part of one problem with is considered a collaborator.}
\normalsize
\mline
\begin{enumerate}[label={\bf {\arabic*}:}]
\item From A\&F: 2.4.2 c, e.\\
Evaluate the integral $\oint_Cf(z)\D z$, where C is the unit circle enclosing the origin, and $f(z)$ is given as follows: \\
c) $$f(z) = \frac {1} {\bar z}$$
\textit{Solution:} \\
e) $$f(z) = e^{\bar z}$$
\textit{Solution:} \\
\item From A\&F: 2.4.4 a, b.
Use the principal branch where the argument is in $[-\pi,\pi)$.
Discuss any ambiguities. 
Use the principal branch of $\log(z)$ and $z^{\frac{1}{2}}$ where the argument is in $[-\pi,\pi)$ to evaluate the following: \\
a) $$\int_{-1}^{1}\log z \D z$$
\textit{Solution:} \\
b) $$\int_{-1}^{1}z^{\frac{1}{2}} \D z$$
\textit{Solution:} \\
\item From A\&F: 2.4.7 \\
Let C be an open (upper) semicircle of radius $R$ with its center at the origin, and consider $\int_C f(z) \D z$.
 Let $f(z) = \frac{1}{z^2 + a^2}$ for a real $a > 0$.
Show that $\left| f(z) \right| \leq \frac{1}{R^2 - a^2}$, $R > a$, and
$$
\left| \int_C f(z) dz \right| \leq \frac{\pi R}{R^2 - a^2}, \quad R > a.
$$
\textit{Solution:} \\
\item From A\&F: 2.4.8 \\
Let $C$ be an arc of the circle $\left|z\right| = R(R > 1)$ of angle $\frac{\pi}{3}$.
Show that 
$$
\left| \int_C \frac{\D z}{z^3 + 1} \right| \leq \frac \pi 3 \left( \frac{R}{R^3 - 1} \right)
$$
and deduce
$$
\lim_{R \rightarrow \infty} \int_C \frac{\D z}{z^3 + 1} = 0
$$
\textit{Solution:} \\
\item From A\&F: 2.5.1 b, e \\
Evaluate $\oint_C f(z)\D z$, where $C$ is the unit circle centered at the origin, and $f(z)$ is given by the following: \\
b) $$f(z) = \E^{z^2}$$ \\
\textit{Solution:} \\
e) $$f(z) = \frac{1}{2z^2 + 1} $$ \\
\textit{Solution:} \\
\item Use the ideas from A\&F: 2.5.5 to evaluate $\int_0^\infty \E^{\I
    z^3 t} \D z$, $t > 0$.  Express the result in terms of $\int_0^\infty \E^{-
    r^3} \D r$. \\
The ideas we might need to use are ... it's actually really long! \\
\textit{Solution:}\\
\item From A\&F: 2.5.6. \\
Consider the integral $$I = \int_{-\infty}^{\infty} \frac{\D x}{x^2 + 1}.$$
Show how to evaluate this integral by considering
$$\oint_{C_{(\mathbb R)}} \frac{\D z}{z^2 + 1},$$
where $C_{(\mathbb R)}$ is closed semicircle in the upper half plane with endpoints at $(-R, 0)$ and $(R, 0)$ plus the $x$-axis.
\textit{Hint:} use
$$\frac{1}{z^2 + 1} = -\frac{1}{2i}\left(\frac{1}{z + i} - \frac{1}{z - i}\right),$$
and show that the integral along the open semicircle in the upper half plane vanishes as $R \rightarrow \infty$.
Verify your answer by usual integration in real variables.
\textit{Solution:}\\
\\

\noindent
Repeat this exercise for
  \begin{align*}
    I_\epsilon = \int_{-\infty}^\infty \frac{\epsilon \D x}{x^2 +
    \epsilon^2}, \quad \epsilon > 0.
  \end{align*}\\
Seems like I am supposed to do 2.5.6 and then for the given integral as well. \\
\textit{Solution:}\\
\item Use a similar method to calculate
  $\int_{-\infty}^{\infty} \frac{d x}{1+x^4}$. \\
\textit{Solution:}\\

\item From A\&F: 2.6.1 a, e.\\
Evaluate the integrals $\oint_C f(z) \D z$, where $C$ is the unit circle centered at the origin and $f(z)$ is given by the following (use Eq. (1.2.19) as necessary): \\
a)
$$
\frac{\sin z}{z}
$$
\\
\textit{Solution:}\\
e)
$$
\E^{z^2}\left(\frac{1}{z^2} - \frac{1}{z^3}\right)
$$
\\
\textit{Solution:}\\
\end{enumerate}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
